Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-06 arxiv/diff_cov.tex
section 4 edit

Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
Consider the prediction loss if we fix $n_2$ and increase $n_1$.
We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
We describe an informal proof.
First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
%Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
%(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
%(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
%(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.

>>>>

Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
Consider the prediction loss if we fix $n_2$ and increase $n_1$.
We show that as a function of $n_1$, the limit equation always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ with $n_1$ going to infinity.
We describe an informal proof.
First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Moreover, near the point where $n_1$ is zero, one can verify that bias increases less than the decrease in variance, and there is only one positive root for the derivative being zero.
%Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
%(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
%(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
%(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
The proof of Corollary \ref{cor_MTL_loss} can be found in Appendix \ref{app_iso_cov}.
